---
title: "Genotype EDA"
pagetitle: "Genotype EDA | dnaprs"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
suppressWarnings(suppressPackageStartupMessages({
  library(data.table)
  library(knitr)
}))
```

```{r, include=FALSE}
source("report-setup.R", local = knitr::knit_global())
```

## Target

These results describe the supplied input before preparation. Diagnostic marker subsets
do not change the source genotypes or remove participants. Corrected checks and scoring
decisions appear in [Target QC](target-qc.qmd).

```{r}
tableVIEW(
  genotypeEDA[, intersect(c(
    "cohort", "role", "input_stage", "format", "participants", "variants", "chromosomes",
    "autosomal_variants", "x_variants", "y_variants", "mitochondrial_variants",
    "unplaced_or_nonstandard_variants", "recorded_sex_participants",
    "phenotype_participants", "duplicated_participant_identifiers",
    "duplicated_variant_identifier_groups", "pass_items", "review_items", "fail_items",
    "not_run_items", "completion", "status", "recorded_status"
  ), names(genotypeEDA)), with = FALSE],
  "Supplied target composition by declared cohort."
)
```

## Runs

`PASS` means the check completed without flagged findings. `REVIEW` means it completed
with findings to inspect. `FAIL` means an attempted calculation failed or produced invalid
required values. `NOT_RUN` means it was not attempted; the reason identifies unavailable
inputs or a failed prerequisite. Any failed check makes the overall status `FAIL`.
Skipped checks are shown as partial coverage, not successful calculations. A raw failure
remains visible even if the later corrected check succeeds.
For older results, `recorded_status` preserves an original status that differs from
the displayed status. An attempted calculation recorded as `NOT_RUN` is displayed as
`FAIL` only when its recorded reason confirms that it failed. Source results are unchanged.

```{r}
tableVIEW(
  genotypeEDACHECK,
  "Exploratory checks, including explicit reasons when a diagnostic could not be run."
)
```

## Figures

```{r, results='asis'}
figureGALLERY("Genotype EDA")
```

## Results

```{r}
fileTABLE(
  "^(genotype_eda|logs/genotype_eda)",
  "Genotype EDA summaries, exact figure-source tables, PLINK diagnostics, and the complete stage log."
)
```

<div class="dnaprs-closing-card">
<p>The supplied target structure supports continued preparation when format import passes and every unavailable or unusual diagnostic has an explicit record. REVIEW results remain visible for Target PREP and Target QC; this exploratory stage does not silently remove participants or variants.</p>
</div>
