---
title: "GWAS QC"
pagetitle: "GWAS QC | dnaprs"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
suppressWarnings(suppressPackageStartupMessages({library(data.table); library(knitr)}))
```

```{r, include=FALSE}
source("report-setup.R", local = knitr::knit_global())
```

## Discovery studies

```{r}
tableVIEW(gwasMANIFEST, "Declared discovery studies, effect definitions, builds, and source fields.")
```

## Diagnostics and filtering

```{r, results='asis'}
figureGALLERY("GWAS QC")
```

```{r}
tableVIEW(gwasSUMMARY, "GWAS source and post-QC variant counts.")
```

## Method-ready outputs

```{r}
fileTABLE("^(gwas|qc/gwas)/", "Harmonised GWAS fields, clumping inputs, and structural QC summaries.")
```

<div class="dnaprs-closing-card">
<p>A passed GWAS QC result means the declared records have valid scoring fields, one row per variant identifier, and an auditable effect scale. It does not repeat discovery-consortium participant QC, establish target allele compatibility by itself, or prove phenotype prediction; method-specific reference alignment and target score coverage remain downstream evidence.</p>
</div>
