---
title: "Overview"
pagetitle: "Overview | dnaprs"
body-classes: dnaprs-overview-page
---

```{r setup, include=FALSE}
# Configure rendering and load the report packages.
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
suppressWarnings(suppressPackageStartupMessages({
  library(data.table)
  library(knitr)
}))
```

```{r, include=FALSE}
# Load the completed results and shared report controls.
source("report-setup.R", local = knitr::knit_global())
```

<div class="dnaprs-hero">
<img src="assets/nf-core-dnaprs_logo_light.svg" alt="dnaprs" data-dnaprs-logo />
</div>

<div class="dnaprs-opening-card">
<p><strong>dnaprs</strong> prepares target genotypes and GWAS summary statistics, evaluates their quality, and generates polygenic risk scores with <strong>PLINK</strong> clumping and thresholding, <strong>SBayesRC</strong>, or both methods. The report records the data, reference resources, decisions, score calculations, phenotype associations, and software used in this run. The phenotype is not used to select variants or tune the PRS methods.</p>
</div>

<div class="dnaprs-kpis">
<div class="dnaprs-kpi"><strong>`r uniqueN(score$cohort)`</strong><span>Cohorts</span></div>
<div class="dnaprs-kpi"><strong>`r uniqueN(score[, .(cohort, IID)])`</strong><span>Participants</span></div>
<div class="dnaprs-kpi"><strong>`r uniqueN(score$trait_id)`</strong><span>PRS traits</span></div>
<div class="dnaprs-kpi"><strong>`r uniqueN(score$method)`</strong><span>Methods</span></div>
</div>

## Summary

```{r, results='asis'}
figureGALLERY("Overview")
```

## Runs

```{r}
# Display the checks completed before PRS calculation.
buttonROW(fileBUTTON("input_checks.tsv", filename = "runs.tsv"))
tableVIEW(inputCHECK, "Input and run checks completed before PRS calculation.")
```

## Scores

```{r}
# Display participant counts, scoring coverage, and final score status.
buttonROW(fileBUTTON("score_qc.tsv", filename = "scores.tsv"))
tableVIEW(
  scoreQC[, .(
    cohort,
    prs_name,
    method = method_label,
    participants,
    used_variants,
    status
  )],
  "Participant score checks and within-cohort scaling."
)
```

<div class="dnaprs-closing-card">
<p>The technical checks establish that the declared inputs were processed consistently and that every reported score can be traced to its GWAS, reference resources, target variants, and software. Phenotype associations describe research agreement in the analysed cohort. They do not make the scores clinical risk estimates or provide independent predictive validation.</p>
</div>
