---
title: "Overview"
pagetitle: "Overview | dnaprs"
body-classes: dnaprs-overview-page
---

```{r setup, include=FALSE}
# Configure rendering and load the report packages.
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
suppressWarnings(suppressPackageStartupMessages({
  library(data.table)
  library(knitr)
}))
```

```{r, include=FALSE}
# Load the completed results and shared report controls.
source("report-setup.R", local = knitr::knit_global())
```

<div class="dnaprs-hero">
<img src="assets/nf-core-dnaprs_logo_light.svg" alt="dnaprs" data-dnaprs-logo />
<div>
<p class="dnaprs-eyebrow">POLYGENIC RISK SCORE REPORT</p>
<h1>Reproducible score generation and review</h1>
</div>
</div>

<div class="dnaprs-opening-card">
<p>dnaprs prepares target genotypes and GWAS summary statistics, evaluates their quality, and generates polygenic risk scores with PLINK clumping and thresholding, SBayesRC, or both methods. The report records the data, reference resources, decisions, score calculations, phenotype associations, and software used in this run. The phenotype is not used to select variants or tune the PRS methods.</p>
</div>

<div class="dnaprs-kpis">
<div class="dnaprs-kpi"><strong>`r uniqueN(score$cohort)`</strong><span>Cohorts</span></div>
<div class="dnaprs-kpi"><strong>`r uniqueN(score[, .(cohort, IID)])`</strong><span>Participants</span></div>
<div class="dnaprs-kpi"><strong>`r uniqueN(score$trait_id)`</strong><span>PRS traits</span></div>
<div class="dnaprs-kpi"><strong>`r uniqueN(score$method)`</strong><span>Methods</span></div>
</div>

## Run-level quantitative summary

```{r, results='asis'}
figureGALLERY("Overview")
```

## Analysis summary

<div class="dnaprs-summary-grid">
<section class="dnaprs-card">
<h3>Target and GWAS</h3>
<p>The report records genome build, target cohorts, GWAS studies, reference resources, allele alignment, and variant retention.</p>
</section>
<section class="dnaprs-card">
<h3>PRS generation</h3>
<p>`r paste(unique(score$method_label), collapse = " and ")` scores were calculated for `r uniqueN(score$trait_id)` trait(s). Variant coverage and participant-level score checks are recorded below.</p>
</section>
<section class="dnaprs-card">
<h3>Phenotype analysis</h3>
<p>`r if (nrow(association)) paste0(uniqueN(association$model_id), " prespecified model(s) were evaluated.") else "No phenotype model was run."` These estimates describe research association, not clinical prediction.</p>
</section>
</div>

## Run checks

```{r}
# Display the checks completed before PRS calculation.
buttonROW(fileBUTTON("input_checks.tsv", "Download run checks"))
tableVIEW(inputCHECK, "Input and run checks completed before PRS calculation.")
```

## Score checks

```{r}
# Display participant counts, scoring coverage, and final score status.
buttonROW(fileBUTTON("score_qc.tsv", "Download score checks"))
tableVIEW(
  scoreQC[, .(
    cohort,
    prs_name,
    method = method_label,
    participants,
    used_variants,
    status
  )],
  "Participant score checks and within-cohort scaling."
)
```

<div class="dnaprs-closing-card">
<p>The technical checks establish that the declared inputs were processed consistently and that every reported score can be traced to its GWAS, reference resources, target variants, and software. Phenotype associations describe research agreement in the analysed cohort. They do not make the scores clinical risk estimates or provide independent predictive validation.</p>
</div>
