---
title: "Overview"
pagetitle: "Overview | dnaprs"
body-classes: dnaprs-overview-page
---

```{r setup, include=FALSE}
# Configure rendering and load the report packages.
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
suppressWarnings(suppressPackageStartupMessages({
  library(data.table)
  library(knitr)
}))
```

```{r, include=FALSE}
# Load the completed results and shared report controls.
source("report-setup.R", local = knitr::knit_global())
```

<div class="dnaprs-hero">
<img src="assets/nf-core-dnaprs_logo_light.svg" alt="nf-core/dnaprs" data-dnaprs-logo />
<div>
<p class="dnaprs-eyebrow">POLYGENIC RISK SCORE REPORT</p>
<h1>Reproducible score generation and review</h1>
<p>This website records the inputs, score-generation checks, quantitative figures, phenotype associations, and files produced by the completed run.</p>
</div>
</div>

The score-generation checks are separate from phenotype associations. Phenotypes are
not used to choose variants, PLINK thresholds, or SBayesRC weights.

<div class="dnaprs-kpis">
<div class="dnaprs-kpi"><strong>`r uniqueN(score$cohort)`</strong><span>Cohorts</span></div>
<div class="dnaprs-kpi"><strong>`r uniqueN(score[, .(cohort, IID)])`</strong><span>Participants</span></div>
<div class="dnaprs-kpi"><strong>`r uniqueN(score$trait_id)`</strong><span>PRS traits</span></div>
<div class="dnaprs-kpi"><strong>`r uniqueN(score$method)`</strong><span>Methods</span></div>
</div>

## Analysis summary

<div class="dnaprs-summary-grid">
<section class="dnaprs-card">
<h3>Target and GWAS</h3>
<p>The report records genome build, target cohorts, GWAS studies, reference resources, allele alignment, and variant retention.</p>
</section>
<section class="dnaprs-card">
<h3>PRS generation</h3>
<p>`r paste(unique(score$method_label), collapse = " and ")` scores were calculated for `r uniqueN(score$trait_id)` trait(s). Variant coverage and participant-level score checks are recorded below.</p>
</section>
<section class="dnaprs-card">
<h3>Phenotype analysis</h3>
<p>`r if (nrow(association)) paste0(uniqueN(association$model_id), " prespecified model(s) were evaluated.") else "No phenotype model was run."` These estimates describe research association, not clinical prediction.</p>
</section>
</div>

## Run checks

```{r}
# Display the checks completed before PRS calculation.
buttonROW(fileBUTTON("preflight_qc.tsv", "Download run checks"))
tableVIEW(preflight, "Input and run checks completed before PRS calculation.")
```

## Score checks

```{r}
# Display participant counts, scoring coverage, and final score status.
buttonROW(fileBUTTON("score_qc.tsv", "Download score checks"))
tableVIEW(
  scoreQC[, .(
    cohort,
    prs_name,
    method = method_label,
    participants,
    used_variants,
    status
  )],
  "Participant score checks and within-cohort scaling."
)
```

**Interpretation.** A completed score requires the expected participants, finite values,
and recorded scoring-variant coverage. These checks confirm calculation quality but do
not establish prediction or clinical usefulness.
