---
title: "Logs"
pagetitle: "Logs | dnaprs"
---

```{r setup, include=FALSE}
# Configure rendering and load the report packages.
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
suppressWarnings(suppressPackageStartupMessages({
  library(data.table)
  library(knitr)
}))
```

```{r, include=FALSE}
# Load the completed results and shared report controls.
source("report-setup.R", local = knitr::knit_global())
```

This page groups method logs, software versions, task status, resource use, and the
workflow structure. Full logs are downloaded rather than repeated inside the website.

## Method and software records

```{r}
# Display direct downloads for method logs and software versions.
fileTABLE(
  "^(logs|pipeline_info)",
  "Method logs and software-version records."
)
```

## Nextflow execution

Nextflow completes these files when the run finishes. The execution report summarises
status and resource use; the timeline shows task timing; the trace provides task-level
metrics; and the directed acyclic graph (DAG) records workflow structure.

<div class="dnaprs-log-grid">
<a class="dnaprs-log-card" href="provenance/execution_report.html"><strong>Execution report</strong><span>Run summary, resources, and task status</span></a>
<a class="dnaprs-log-card" href="provenance/execution_timeline.html"><strong>Execution timeline</strong><span>Scheduling and execution time by task</span></a>
<a class="dnaprs-log-card" href="provenance/pipeline_dag.html"><strong>Pipeline DAG</strong><span>Processes and their data connections</span></a>
<a class="dnaprs-log-card" href="provenance/execution_trace.tsv" download><strong>Task trace</strong><span>Download detailed task metrics</span></a>
<a class="dnaprs-log-card" href="provenance/report_software_versions.tsv" download><strong>Report software</strong><span>Download report software versions</span></a>
</div>
