---
title: "Phenotype"
pagetitle: "Phenotype | dnaprs"
---

```{r setup, include=FALSE}
# Configure rendering and load the report packages.
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
suppressWarnings(suppressPackageStartupMessages({
  library(data.table)
  library(knitr)
}))
```

```{r, include=FALSE}
# Load the completed results and shared report controls.
source("report-setup.R", local = knitr::knit_global())
```

Phenotype models evaluate the prespecified association between each psychological
phenotype and its matching PRS while accounting for the declared covariates. The
phenotype results do not change the PRS weights or scoring settings.

## Quantitative review

```{r, results='asis'}
# Display phenotype estimates and model checks in one figure gallery.
figureGALLERY("Phenotype")
```

**Interpretation.** Effect estimates, confidence intervals, added model fit, adjusted
patterns, and diagnostics should be interpreted together. In a small sample, uncertainty
and individual observations can be more informative than a P value alone.

## Association estimates

```{r}
# Display the prespecified matching phenotype and PRS associations.
associationTABLE <- addMETHODLABEL(copy(association))
tableVIEW(
  associationTABLE[, .(
    model_id,
    cohort,
    method = method_label,
    n,
    beta,
    ci_low,
    ci_high,
    p_value,
    incremental_fit,
    fit_metric,
    status
  )],
  "Prespecified matching phenotype and PRS associations."
)
```

## Fitted models

```{r}
# Display the exact model formulas and estimators used by the pipeline.
tableVIEW(
  fittedMODEL[, .(
    model_id,
    cohort,
    method,
    estimator,
    formula,
    null_formula,
    primary
  )],
  "Exact phenotype models fitted by the pipeline."
)
```

## Phenotype result files

The complete tables contain participant-level research data and should remain in the
restricted result directory.

```{r}
# Provide the association, fitted-model, and plot-data files.
buttonROW(
  fileBUTTON("phenotype_associations.tsv", "Download associations"),
  fileBUTTON("phenotype_models_fitted.tsv", "Download fitted formulas"),
  fileBUTTON("phenotype_plot_data.tsv", "Download plot data")
)
```
