---
title: "Phenotype"
pagetitle: "Phenotype | dnaprs"
---

```{r setup, include=FALSE}
# Configure rendering and load the report packages.
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
suppressWarnings(suppressPackageStartupMessages({
  library(data.table)
  library(knitr)
}))
```

```{r, include=FALSE}
# Load the completed results and shared report controls.
source("report-setup.R", local = knitr::knit_global())
```

## Figures

```{r, results='asis'}
# Display phenotype estimates and model checks in one figure gallery.
figureGALLERY("Phenotype")
```

## Scores

```{r, results='asis'}
tableVIEW(reportTABLESOURCE("^phenoPRS[.]csv$"), "Original phenotype rows with raw and standardised PRSs, QC flags and scoring eligibility. Excluded participants have no score.")
```

## Estimates

```{r}
# Display the prespecified matching phenotype and PRS associations.
associationTABLE <- addMETHODLABEL(copy(association))
tableVIEW(
  associationTABLE[, .(
    model_id,
    cohort,
    method = method_label,
    participants,
    beta,
    ci_low,
    ci_high,
    parametric_p,
    permutation_p,
    permutation_holm,
    permutation_scheme,
    permutations,
    delta_r2,
    partial_r2,
    fit_metric,
    status
  )],
  "Prespecified matching phenotype and PRS associations."
)
```

## Models

```{r}
# Display the exact model formulas and estimators used by the pipeline.
tableVIEW(
  fittedMODEL[, .(
    model_id,
    cohort,
    method,
    estimator,
    formula,
    null_formula,
    primary
  )],
  "Exact phenotype models fitted by the pipeline."
)
```

## Results

```{r, results='asis'}
# Provide the association, fitted-model, and plot-data files.
fileTABLE("^phenotype(/|$)", "Phenotype analysis tables.", exclude = "^phenoPRS[.]csv$")
```

<div class="dnaprs-closing-card">
<p>The PRS coefficient describes the expected phenotype difference per one target-cohort PRS standard deviation after accounting for the declared covariates. Change in model fit shows how much additional variation is described after adding the PRS. In a small sample, confidence intervals, permutation results, and leave-one-participant-out changes are interpreted together. These are research associations and not independent clinical validation.</p>
</div>
