---
title: "Phenotype"
pagetitle: "Phenotype | dnaprs"
---

```{r setup, include=FALSE}
# Configure rendering and load the report packages.
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
suppressWarnings(suppressPackageStartupMessages({
  library(data.table)
  library(knitr)
}))
```

```{r, include=FALSE}
# Load the completed results and shared report controls.
source("report-setup.R", local = knitr::knit_global())
```

## Quantitative review

```{r, results='asis'}
# Display phenotype estimates and model checks in one figure gallery.
figureGALLERY("Phenotype")
```

Effect estimates, confidence intervals, added model fit, adjusted patterns, and
diagnostics should be interpreted together. In a small sample, uncertainty and
individual observations can be more informative than a P value alone.

## Association estimates

```{r}
# Display the prespecified matching phenotype and PRS associations.
associationTABLE <- addMETHODLABEL(copy(association))
tableVIEW(
  associationTABLE[, .(
    model_id,
    cohort,
    method = method_label,
    n,
    beta,
    ci_low,
    ci_high,
    p_value,
    empirical_p,
    permutation_scheme,
    permutations,
    incremental_fit,
    fit_metric,
    status
  )],
  "Prespecified matching phenotype and PRS associations."
)
```

## Fitted models

```{r}
# Display the exact model formulas and estimators used by the pipeline.
tableVIEW(
  fittedMODEL[, .(
    model_id,
    cohort,
    method,
    estimator,
    formula,
    null_formula,
    primary
  )],
  "Exact phenotype models fitted by the pipeline."
)
```

## Phenotype result files

The complete tables contain participant-level research data and should remain in the
restricted result directory.

```{r}
# Provide the association, fitted-model, and plot-data files.
buttonROW(
  fileBUTTON("phenoPRS.csv", "Download phenoPRS.csv"),
  fileBUTTON("phenotype_associations.tsv", "Download associations"),
  fileBUTTON("phenotype_models_fitted.tsv", "Download fitted formulas"),
  fileBUTTON("phenotype_plot_data.tsv", "Download plot data"),
  fileBUTTON("phenotype_permutations.tsv", "Download permutations"),
  fileBUTTON("phenotype_influence.tsv", "Download influence diagnostics")
)
```

<div class="dnaprs-closing-card">
<p>The PRS coefficient describes the expected phenotype difference per one target-cohort PRS standard deviation after accounting for the declared covariates. Change in model fit shows how much additional variation is described after adding the PRS. In a small sample, confidence intervals, permutation results, and leave-one-participant-out changes are interpreted together. These are research associations and not independent clinical validation.</p>
</div>
