---
title: "PLINK PRS"
pagetitle: "PLINK PRS | dnaprs"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
suppressWarnings(suppressPackageStartupMessages({library(data.table); library(knitr)}))
```

```{r, include=FALSE}
source("report-setup.R", local = knitr::knit_global())
```

## Variant retention

```{r}
tableVIEW(
  variantFLOW[method == "plink_ct", .(
    cohort, trait_id, prs_name, stage, variant_count, percent_of_source
  )],
  "PLINK candidate, clumped, and scored variant counts."
)
```

## Target coverage and participant PRS review

```{r, results='asis'}
figureGALLERY("PLINK PRS")
```

## Imputation sensitivity

```{r}
tableVIEW(plinkSENSITIVITYQC, "Typed/imputed scoring-variant coverage and participant-score agreement.")
```

```{r}
tableVIEW(plinkSENSITIVITY, "Participant-level standardised score comparison between the imputed and direct-genotype checkpoints.")
```

## Outputs and downloads

```{r}
fileTABLE(
  "^(plink_ct|reference/plink_ct|qc/plink_ct|qc/scores|scores|logs/plink_ct)",
  "PLINK reference frequencies, clumps, ALT-aligned weights, participant scores, checks, and logs."
)
```

<div class="dnaprs-closing-card">
<p>A passed PLINK score requires a non-empty weight set, recorded variant coverage, one finite score for every eligible participant, and an auditable allele direction. Typed and imputed contributions show where the genetic information came from. These checks establish calculation quality but do not by themselves establish prediction or clinical validity.</p>
</div>
