---
title: "PRS"
pagetitle: "PRS | dnaprs"
---

```{r setup, include=FALSE}
# Configure rendering and load the report packages.
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
suppressWarnings(suppressPackageStartupMessages({
  library(data.table)
  library(knitr)
}))
```

```{r, include=FALSE}
# Load the completed results and shared report controls.
source("report-setup.R", local = knitr::knit_global())
```

The polygenic risk score (PRS) figures show variant coverage, every participant score,
relationships among scores, and agreement between methods when both methods were run.

## Quantitative review

```{r, results='asis'}
# Display the PRS figure gallery with contextual downloads.
figureGALLERY("PRS")
```

**Interpretation.** The figures can identify missing scores, unusual observations,
shared information among traits, and differences between methods. These patterns support
quality review but do not by themselves establish predictive validity.

## Score checks

```{r}
# Display participant counts and scoring coverage for each completed score.
tableVIEW(
  scoreQC[, .(
    cohort,
    trait_id,
    prs_name,
    method = method_label,
    participants,
    used_variants,
    status
  )],
  "Participant score checks and scoring coverage."
)
```

## Method agreement

```{r}
# Display the calculated agreement statistics when both methods were run.
if (nrow(concordance) > 0L) {
  buttonROW(fileBUTTON("method_concordance.tsv", "Download method agreement"))
  tableVIEW(concordance, "Participant-score agreement between methods.")
}
```

## Participant score files

The files contain participant-level research data and should remain in the restricted
result directory.

```{r}
# Provide the complete long and wide score tables beside their quality record.
buttonROW(
  fileBUTTON("prs_scores_long.tsv", "Download long PRS table"),
  fileBUTTON("prs_scores_wide.tsv", "Download wide PRS table"),
  fileBUTTON("score_qc.tsv", "Download score checks")
)
```
