---
title: "SBayesRC PRS"
pagetitle: "SBayesRC PRS | dnaprs"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
suppressWarnings(suppressPackageStartupMessages({library(data.table); library(knitr)}))
```

```{r, include=FALSE}
source("report-setup.R", local = knitr::knit_global())
```

## Alignment, imputation, and model counts

```{r}
tableVIEW(
  variantFLOW[method == "sbayesrc", .(
    cohort, trait_id, prs_name, stage, variant_count, percent_of_source
  )],
  "SBayesRC alignment, summary-imputation, model, and scoring counts."
)
```

## Target coverage and participant PRS review

```{r, results='asis'}
figureGALLERY("SBayesRC PRS")
```

## Outputs and downloads

```{r}
fileTABLE(
  "^(sbayesrc|qc/sbayesrc|qc/scores|scores|logs/sbayesrc)",
  "SBayesRC tidy, summary-imputed, model, participant-score, quality, and log files."
)
```

<div class="dnaprs-closing-card">
<p>A passed SBayesRC result requires successful reference alignment, summary imputation, joint-model completion, valid posterior weights, non-zero target coverage, and one finite score per eligible participant. The phenotype analysis remains separate and does not alter the model or weights.</p>
</div>
