---
title: "Target QC"
pagetitle: "Target QC | dnaprs"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
suppressWarnings(suppressPackageStartupMessages({library(data.table); library(knitr)}))
```

```{r, include=FALSE}
source("report-setup.R", local = knitr::knit_global())
```

## Scoring readiness

```{r, results='asis'}
figureGALLERY("Target QC")
```

```{r}
tableVIEW(targetQC, "Final target dimensions and scoring-readiness status.")
```

## Participant decisions

```{r}
tableVIEW(targetSAMPLEDECISION, "Participant-level missingness decisions; heterozygosity, sex, relatedness, and PCA remain review evidence in Genotype EDA.")
```

```{r}
tableVIEW(participantDECISION, "Integrated technical-QC, relatedness, reference-ancestry, score-eligibility, and primary-analysis decisions.")
```

## Reference ancestry

```{r}
tableVIEW(ancestrySUMMARY, "Reference matching, PCA, empirical European distance threshold, and target classification summary.")
```

```{r}
tableVIEW(targetANCESTRY, "Target participant projections and explicit ancestry classifications.")
```

## Variant decisions

```{r}
tableVIEW(targetVARIANTDECISION, "Variant-level missingness, allele, chromosome, MAF, and HWE decisions.")
```

## Outputs and downloads

```{r}
fileTABLE("^target_qc/", "Target QC summaries and participant/variant decision tables.")
```

<div class="dnaprs-closing-card">
<p>A passed Target QC summary means the raw or corrected checkpoint was evaluated with the declared technical thresholds and produced non-empty autosomal PGEN output. Reference ancestry and relatedness are recorded as explicit participant decisions: technically eligible participants remain available for sensitivity analysis, while the primary analysis uses the declared ancestry and unrelated-participant rules.</p>
</div>
