---
title: "Target and GWAS"
pagetitle: "Target and GWAS | dnaprs"
---

```{r setup, include=FALSE}
# Configure rendering and load the report packages.
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
suppressWarnings(suppressPackageStartupMessages({
  library(data.table)
  library(knitr)
}))
```

```{r, include=FALSE}
# Load the completed results and shared report controls.
source("report-setup.R", local = knitr::knit_global())
```

This page records how many GWAS variants remain after harmonisation, reference
alignment, method-specific modelling, and target scoring. Counts use a logarithmic
scale because the source and final scoring counts can differ by several orders of
magnitude.

## Variant flow

```{r, results='asis'}
# Display the quantitative variant-flow figure and its downloads.
figureGALLERY("Target and GWAS")
```

**Interpretation.** Review large unexpected losses and differences between traits or
methods. SBayesRC summary imputation can increase the count after reference alignment;
that increase is displayed rather than treated as retained source variants.

## Variant counts

```{r}
# Display the exact counts represented by the variant-flow figure.
tableVIEW(
  variantFLOW[, .(
    cohort,
    trait_id,
    prs_name,
    method = method_label,
    stage,
    variant_count,
    percent_of_source
  )],
  "Variant retention across PRS generation."
)
```

## Target and GWAS files

```{r}
# Provide target and GWAS results beside their descriptions.
fileTABLE("^(qc/target|qc/gwas|gwas/)", "Target and GWAS results.")
```
